Berkeley Police Stop Data Maps

### 2016-08-06 eda/Heatmap/HeatmapExploration.Rmd

```{r}
library(sp)
library(ggmap)
library(tidyr)
library(dplyr)
library(stringr)
library(lubridate)
library(ggplot2)
library(readr)
library(maps)
library(mapdata)
library(rgdal)
library(rgeos)
#library(gpclib)       # loads polygon clipping library
library(maptools)     # loads sp library too
library(RColorBrewer) # creates nice color schemes
library(classInt)     # finds class intervals for continuous variables
library(gdata)
library(XLConnect)
library(data.table)
```

### Set data file names:
```{r}
# data file names:
data_file <- "../../clean_data/StopData_merged2.rds" # use the cleaned version of StopData_merged.rds for plotting. See StopData_clean_merged_rds.R for more information.
census_tract_folder <- "../../raw_data/Census_Tract_Polygons2010"
census_tract_shp <- "Census_tracts_2010"
census_tract_csv <- "../../raw_data/Census_tracts_2010.csv"
alameda_xls <- "../../raw_data/2010_Pop_Block_County.xls"
alameda_tract_nums_xls <- "../../raw_data/census_tract_numbers.xls"

### Read in the data:
```{r}
# read in the data to modify:
df <- readRDS( data_file )
wb <- loadWorkbook(alameda_xls)
alameda <- readWorksheet(wb, sheet=1,startRow = 5) 
```

@@

### Get the regular Berkeley map:
```{r}
# get the plain Berkeley map from Google:
berkMap = map = get_map(location = c( lon = mean(lonvals), lat = mean(latvals) ), zoom = 12)
```

@@

# First read in the shapefile, using the path to the shapefile and the shapefile name minus the
# extension as arguments
# Next the shapefile has to be converted to a dataframe for use in ggplot2
shapefile_df <- fortify(censusT)

@@

@@

### WORKs:
```{r}
# READ IN DATA RIGHT!!!
census.df <- fortify(census2, region = 'GEOID10')
pop <- read.csv(file=census_tract_csv, header = TRUE)
names(pop)[13] <- "id"
pop <- pop %>%
  select(GEOID10, id, TotalPop) %>% 
  mutate( id = str_c("0", as.character(id)) ) 
census.df_pop <- left_join(census.df, pop, by = "id")
```

```{r}
popdenmap <- ggmap(berkMap) + 
  geom_polygon(data = census.df_pop, aes(x = long, y = lat, group = group, fill = TotalPop), color = "white", alpha = .7) 
popdenmap
```

```{r}
popdenmap <- popdenmap + theme_bw()
```

```{r}
popdenmap  +
  coord_fixed(1.3) 
```

```{r}
popdenmap <- popdenmap +
  ditch_the_axes 
popdenmap
```

```{r}
popdenmap + scale_fill_gradient(trans = "log10")
```

```{r}
popamts <- censusCSV$TotalPop
popmin <- min(popamts)
popmin
popmax <- max(popamts)
popmax

#popints <- diff(range(popamts))

popints <- (popamts - min(popamts))/diff(range(popamts)) # recorts the percentage difference from the minimum population

popints_df

@@

```{r}
pd2 <- elbow_room1 + 
    scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(2, 4, 10, 100, 1000, 10000),
                         trans = "log10") 
pd2
```

@@

### Dealing with population info:
```{r}
#write.csv(alameda, file = "alameda_population_by_tract.csv")
alameda = alameda[-1,]
rownames(alameda) <- 1:nrow(alameda)
names(alameda)[1] <- "GEO"

alameda2 <- alameda %>%
  separate(GEO, c("Block","Group", "Tract", "County", "State"), ", ")

names(alameda2)[3] <- "NAME10"

alameda2 <- alameda2 %>%
  mutate(NAME10 = str_replace(NAME10, "Census Tract ", ""))

alameda2 <- alameda2 %>%
  select(-Block,-Group,-County,-State)

a3 <- alameda2 %>%
        group_by(NAME10)%>% 
        summarise(Total.population = sum(Total.population),
                  Hispanic.or.Latino = sum(Hispanic.or.Latino),
                  Total.population..not.Hispanic.or.Latino = sum(Total.population..not.Hispanic.or.Latino),
                  One.race.total = sum(One.race.total),
                  White = sum(White),
                  American.Indian.and.Alaska.Native = sum(American.Indian.and.Alaska.Native),
                  Asian = sum(Asian),
                  Native.Hawaiian.and.Other.Pacific.Islander = sum(Native.Hawaiian.and.Other.Pacific.Islander),
                  Some.Other.Race = sum(Some.Other.Race),
                  Two.or.More.Races = sum(Two.or.More.Races))

#census_alameda <- left_join(censusCSV, a3, by = "NAMELSAD10")
```

```{r}
# READ IN DATA RIGHT!!!
census.df <- fortify(census2, region = 'NAME10')
pop <- censusCSV
pop <- pop %>%
  select(NAME10, TotalPop) %>%
  mutate(NAME10 = as.character(NAME10))

names(a3)[1] <- "id"
names(pop)[1] <- "id"

pop <- left_join(pop, a3, by = "id")
census.df <- left_join(census.df, pop, by = "id")
write.csv2(a3,"alameda_clean_census.csv")
write.csv2(pop, "berkeley_census_clean.csv")
```

```{r}
popdenmap <- ggmap(berkMap) + 
  geom_polygon(data = census.df, aes(x = long, y = lat, group = group, fill = TotalPop), color = "white", alpha = .7) 
popdenmap
```

>>>>

```{r}
library(sp)
library(ggmap)
library(tidyr)
library(dplyr)
library(stringr)
library(lubridate)
library(ggplot2)
library(readr)
library(maps)
library(mapdata)
library(rgdal)
library(rgeos)
#library(gpclib)       # loads polygon clipping library
library(maptools)     # loads sp library too
library(RColorBrewer) # creates nice color schemes
library(classInt)     # finds class intervals for continuous variables
```

### Set data file names:
```{r}
# data file names:
data_file <- "../../clean_data/StopData_merged2.rds" # use the cleaned version of StopData_merged.rds for plotting. See StopData_clean_merged_rds.R for more information.
census_tract_folder <- "../../clean_data/Census_Tract_Polygons2010"
census_tract_shp <- "Census_tracts_2010"
census_tract_csv <- "../../clean_data/Census_tracts_2010.csv"
```

### Read in the data:
```{r}
# read in the data to modify:
df <- readRDS( data_file )
```

@@

### Get the regular Berkeley map:
```{r}
# get the plain Berkeley map from Google:
berkMap = map = get_map(location = c( lon = mean(lonvals), lat = mean(latvals) ), zoom = 13)
```

@@

# First read in the shapefile, using the path to the shapefile and the shapefile name minus the
# extension as arguments
shapefile <- censusT

# Next the shapefile has to be converted to a dataframe for use in ggplot2
shapefile_df <- fortify(shapefile)

@@

### Some things that didn't work:
```{r}
#usa <- map_data("usa") # we already did this, but we can do it again
# ggmap(berkMap) + geom_polygon(data = census3, aes(x=long, y = lat, group = group)) + 
#   coord_fixed(1.3)

# mappp <- ggmap(berkMap) + 
#   geom_polygon(data = census5, aes(x=lofill = TotalPop), color = "white") +
#   geom_polygon(color = "black", fill = NA) +
#   theme_bw() + 
#   scale_fill_gradient(trans = "log10")
# mappp

# 
# ca_base <- ggmap(berkMap) + ggplot(data = census5, mapping = aes(x = long, y = lat, group = group)) + 
#   coord_fixed(1.3) + 
#   geom_polygon(color = "black", fill = "gray")
# ca_base + theme_nothing()

# ggmap(berkMap) + get_map(census5)
# 
# 
#   stat_density2d(aes(x = long, y = lat, color = TotalPop),
#                  size = 2, bins = 5, data = census5, geom = "polygon") +
#   theme (panel.grid.major = element_blank (), # remove major grid
#          panel.grid.minor = element_blank ()  # remove minor grid
#   ) + 
#   ggtitle("Population Density by Census 2010 Tract Polygons") +
#   labs(alpha = element_blank())

@@

### Sort of works:
```{r}
# census2 <- spTransform(census, CRS("+proj=longlat +datum=WGS84"))
# census3 <- fortify(census2)
# census4 <- read.csv(file=census_tract_csv, header = TRUE)
# census4$id <- 0:32
# census5 <- merge(census3, census4, by='id')
```

```{r}
# READ IN DATA RIGHT!!!
census.df <- fortify(census2, region = 'GEOID10')
pop <- read.csv(file=census_tract_csv, header = TRUE)
names(pop)[13] <- "id"
pop <- pop %>%
  select(GEOID10, id, TotalPop) %>% 
  mutate( id = str_c("0", as.character(id)) ) 
census.df_pop <- left_join(census.df, pop, by = "id")
```

```{r}

@@

```{r}
elbow_room1 <- ggmap(berkMap) + 
  geom_polygon(data = census.df_pop, aes(x = long, y = lat, group = group, fill = TotalPop), color = "white", alpha = .7) 
elbow_room1 
```

```{r}
elbow_room1 <- ggmap(berkMap) + 
  geom_polygon(data = census.df_pop, aes(x = long, y = lat, group = group, fill = TotalPop), color = "white") +
  coord_fixed(1.3) 
elbow_room1 
```

```{r}
elbow_room1 + scale_fill_gradient(trans = "log10")
```

```{r}
eb2 <- elbow_room1 + 
    scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(2, 4, 10, 100, 1000, 10000),
                         trans = "log10") +
  labs(fill = "Total Population")
eb2
```

@@

### 2016-08-06 eda/Location/StopData_Maps.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sp)
library(ggmap)
library(tidyr)
library(plyr)
library(dplyr)
library(stringr)
library(lubridate)
library(ggplot2)
library(readr)
library(data.table)
library(rworldmap)
library(maps)
library(mapdata)
library(maptools)
library(scales)
library(RgoogleMaps)
library(tmap)
library(sp)
library(rgdal)
library(rgeos)
library(RColorBrewer)
#library(raster)
#library(GISTools)
 #library(mgcv)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sp)
library(ggmap)
library(tidyr)
library(plyr)
library(dplyr)
library(stringr)
library(lubridate)
library(ggplot2)
library(readr)
library(data.table)
library(rworldmap)
library(maps)
library(mapdata)
library(maptools)
library(scales)
library(RgoogleMaps)
#library(tmap)
library(sp)
library(rgdal)
library(rgeos)
library(RColorBrewer)
#library(raster)
#library(GISTools)
 #library(mgcv)
```
